Modeling Bandwagoning and Hype in the MLB

### 2020-08-25 Paper_Outline.Rmd
Fixed a little formatting
Fixed some typos in outline

[Abstract]
“Hopping on the bandwagon” is a familiar phrase used to describe a person that follows a trend or believes in an idea solely because it is becoming popular.  The bandwagon effect is very common when describing fans in professional sports, including Major League Baseball. (Talk about Past Bandwagon Studies?) In this work, we model the Google search hits for MLB teams across a season as a function of team success.  Using a hierarchical time series model, we are able to explore which MLB teams attract the most “bandwagon” fans and when MLB teams are overhyped or underhyped? We defined a “hype” moment as an unusual spike in Google searches at a specific time for a team.  The creation of this model required gathering the Google search hits data from Google Trends for each MLB team and collecting other baseball-related data to be used as exogenous variables. (More Model Building) (Results and Conclusion)

>>>>

[Abstract]
“Hopping on the bandwagon” is a familiar phrase used to describe a person that 
follows a trend, believes in an idea, or supports a team solely because it is 
becoming popular. The bandwagon effect is very common when describing fans in 
professional sports, including Major League Baseball. (Talk about Past Bandwagon 
Studies?) In this work, we model the Google search hits for MLB teams across a 
season as a function of team success.  Using a hierarchical time series model, we 
are able to explorewhich MLB teams attract the most “bandwagon” fans and when MLB 
teams are overhypedor underhyped. We defined a “hype” moment as an unusual spike 
in Google searches at a specific time for a team.  The creation of this model 
required gathering the Google search hits data from Google Trends for each MLB 
team and collecting other baseball-related data to be used as exogenous 
variables. (...More Model Building) (...Results and Conclusion)
